Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-10-20 documentation/paper.tex
Added date range of run 2 events
Labeled units and used log scale for audio graph

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{audio}
    \caption{\label{} An example of the cropped audio waveform $\omega$ and full resolution Fourier transform $\beta_{50,001}$.}
\end{figure}

@@

The initial data set $D$ to which these cuts are applied consists of all events recorded during PICO-60 run 2.

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{audio}
    \caption{\label{} An example of the cropped audio waveform $\omega$ and full resolution Fourier transform $\beta_{50,001}$ (recorded on 2016-12-02, run 1, event 21).}
\end{figure}

@@

The initial data set $D$ to which these cuts are applied consists of all events recorded during PICO-60 run 2, between 2016-09-02 and 2017-06-20.
